
Use these functions to describe your dataframe.

### Data frame info {-}

<div class="bluecode">

| Function  |  | Information                                                      |   
|:----------|--|:-----------------------------------------------------------------|
| `glimpse(...)`  |  | rows, columns, column names and a glimpse of values _(from `tidyverse` package)_   |
| `names(scrap)`  |  | column names            |  
| `nrow(...)`     |  | number of rows          |  
| `ncol(...)`     |  | number of columns       | 
| `summary(...)`  |  | summary of all column values (ex. _max_, _mean_, _median_)  | 

</div>


# `glimpse()` & `summary()`
<hr>

### Let's read the scrap data into R and take a look. {-}

`glimpse()` shows the type of data in each column and shows a few sample values.

```{r glimpse-bake, warning=F, message=F}
# Glimpse your dataframe's data types and a few values
glimpse(bake_bots)
```

<br>

`summary()` gives you a quick report of your numeric data.

```{r summary-bake, warning=F, message=F}
# Summary gives us the means, mins, and maxima 
summary(bake_bots)
```

<br>

<div class="tip">
### <i class="fas fa-birthday-cake style="color: gray"></i> Bake it! {-}

Try a few more of the data frame description functions on your bot data. You will need to insert the name of your data frame into each function.

```{r summary-try, eval=F}
nrow( )

ncol( )

names( )
```

</div>

