---
title: "ggplot: Getting fancy"
self_contained: false
output: 
  xaringan::moon_reader:
    lib_dir: libs
    chakra: ../libs/remark-latest.min.js
    seal: false
    includes: 
      in_header: ../css/slide_style.html
    nature:
      slideNumberFormat: ""
      highlightStyle: solarized-light
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
---

```{r setup, include=FALSE}
library(rmarkdown)
library(knitr)
library(magrittr)

xaringanExtra::use_clipboard()

opts_chunk$set(error=TRUE, color=NULL, message=FALSE, warning=FALSE, eval=T, out.height='340px', out.width='130%', dpi=220)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```


class: middle, center, inverse

## .smaller[PLOTS]
# .bigger[.bigger[.teal[GRAMMAR]]]


---

.shift-left[

# Mean flipper lengths

.med-font[
```{r}
flipper_lengths <- all_penguins %>%
                     group_by(species) %>%
                     summarize(flipper_avg = 
                                  mean(flipper_length_mm, na.rm = T))

```
]

<br>

.small-table[
```{r, echo=F}
kable(flipper_lengths)
```
]
]

---

.shift-left[

# Mean flipper lengths

]

.pull-left[
.shift-left[

```{r, eval=F}
ggplot(flipper_lengths, 
       aes(x = species,
           y = flipper_avg))  +
  geom_col(aes(fill = species)) 
```
]]

.pull-right[

```{r, echo=F}
ggplot(flipper_lengths, 
       aes(x = species,
           y = flipper_avg))  +
  geom_col(aes(fill = species))  +
     theme_gray(base_size = 18)
```
]

---
class: inverse, middle, center


# .bigger[.blue[labs( )]]

---
class: inverse, middle, center

# .bigger[.blue[facet_wrap( )]]


---
class: inverse, middle, center

# Legends and scales
# .bigger[.blue[scale_( )]]


---

# Legends and scales

- Hide legends
- Use a color theme
- Use a single color


---
class: inverse, middle, center

# .bigger[.blue[theme( )]]


---
class: inverse, center, middle

# <i class="fas fa-carrot" aria-hidden="true"></i> [Back to Videos](https://tidy-mn.github.io/R-camp-penguins/index.html)
